\documentclass{article}
\usepackage{enumitem}
\usepackage{gensymb}
\usepackage[normalem]{ulem}
\usepackage{fixltx2e}
\usepackage{color}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage[top=2cm,bottom=2cm,left=3cm,right=3cm]{geometry}
\usepackage{multicol}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{longtable}



\begin{document}
\section{Appendix}

\begin{enumerate}

\item Arkin, R. C. (1998).
\\Behavior-based robotics. MIT press, p. 1, 15, 20, 24, 212-213

\item Mark W. Spong and Masayuki Fujita, 2004.
\\Control In Robotics. IEEE Control Systems Society. \\Available: \href{ieeecss.org/sites/ieeecss.org/files/documents/IoCT-Part1-04Robotics.pdf}{\textcolor{blue}{\uline{ieeecss.org/sites/ieeecss.org...}}} [Online]
\\(Accessed 11/11/2014)

\item Stuart J. Russell and Peter Norvig. 2003.
\\Artificial Intelligence: A Modern Approach (2 ed.). Pearson Education.

\item John Kelleher,
\\‘Robot Control Architectures’,  [DT211/1 Applied Computing, DIT School of Computing].
\\Available: \href{www.comp.dit.ie/jkelleher/appliedcomputing/week8/RCA.pdf}{\textcolor{blue}{\uline{www.comp.dit.ie/jkelleher...}}} [Online]
\\(Accessed 11/11/2014)

\item Margaret E. Jefferies, Wai-Kiang Yeap,
\\Robotics and Cognitive Approaches to Spatial Mapping,
\\Volume 38 of Springer Tracts in Advanced Robotics, ISSN 1610-7438. p 175.

\item S. Thrun, D. Fox, W. Burgard, and F. Dellaert,
\\‘Robust monte carlo localization for mobile robots.’ Artificial Intelligence 128,1-2 (2001), 99–141.
\\Available: \href{citeseer.nj.nec.com/thrun01robust.html}{\textcolor{blue}{\uline{citeseer.nj.nec.com/th...}}} [Online]
\\(Accessed 20/11/2014)

\item S. Thrun, D. Fox, W. Burgard,
\\‘Markov localisation for mobile robots in dynamic environments.’ Journal of Artificial Intelligence Research 11 (1999), 391-427.
\\Available: \href{citeseer.nj.nec.com/fox99markov.html}{\textcolor{blue}{\uline{citeseer.nj.nec.com/...}}} [Online]
\\(Accessed 20/11/2014)

\item D. Fox,
\\‘Markov Localisation’ (1999).
\\ Available at: \href{www.cs.cmu.edu/afs/cs/project/jair/pub/volume11/fox99a-html/node2.html}{\textcolor{blue}{\uline{cs.cmu.edu/afs/cs/...}}} [Online]
\\(Accessed 25/11/2014)

\item J. J. Leonard and H. F. Durrant-Whyte,
\\Directed Sonar Sensing for Mobile Robot Navigation, Kluwer Academic, Boston, 1992.

\item B. Schiele and J. L. Crowley,
\\“A comparison of position estimation techniques using occupancy grids,” in Proceedings of IEEE Conference on Robotics and Automation (ICRA), vol. 2, pp. 1628 to 1634, 1994.

\item S. Thrun, D. Fox, W. Burgard, and F. Dellaert, 
\\‘Monte carlo localization for mobile robots.’ Institute of Computer Science III, University of Bonn, D-53117 Bonn.
\\Available at: \href{www.cc.gatech.edu/~dellaert/pub/Dellaert99icra.pdf}{\textcolor{blue}{\uline{www.cc.gatech.edu/...}}} [Online]
\\(Accessed 25/11/2014)

\item ROS.org,
\\‘AMCL Package Summary’,
\\Available: \href{wiki.ros.org/amcl}{\textcolor{blue}{\uline{wiki.ros.org/amcl}}}  [Online]
\\(Accessed 21/10/2014)

\item D. Fox et al,
\\"Particle Filters for Robot Localisation",
\\Available: \href{citeseerx.ist.psu.edu/viewdoc...}{\textcolor{blue}{\uline{citeseerx.ist.psu.edu/viewdoc...}}} [Online]
\\(Accessed 24/11/2014)

\item R. R. Murphy.
\\‘Introduction to AI Robotics’. The MIT Press, Cambridge, Massachusetts, 2000.

\item L. De Silva and H. Ekanayake,
\\“Behavior-based Robotics And The Reactive Paradigm - A Survey”. University of Colombo School of Computing. Proceedings of International Workshop on Data Mining and Artificial Intelligence (DMAI’ 08).
\\Available: \href{www.cs.utah.edu/~alnds/papers/behavior_robotics_2008.pdf}{\textcolor{blue}{\uline{www.cs.utah.edu/\~alnds/p...}}} [Online]
\\(Accessed 27/11/2014)

\item D. Fox,
\\‘Adapting the Sample Size in Particle Filters Through KLD-Sampling‘ . Department of Computer Science, University of Washington.
\\Available: \href{www.cs.washington.edu/robotics/mcl/postscripts/adaptive-ijrr-2003.pdf}{\textcolor{blue}{\uline{www.cs.washington.edu/ro...}}} [Online]
\\(Accessed 27/11/2014)

\item D.Fox,
\\‘KLD-Sampling: Adaptive Particle Filters’, Department of Computer Science, University of Washington.
\\Available: \href{papers.nips.cc/paper/1998-kld-sampling-adaptive-particle-filters.pdf}{\textcolor{blue}{\uline{papers.nips.cc/paper...}}} [Online]
\\(Accessed 27/11/2014).

\item D. Pinto,
\\‘The Kullbach-Liebler Distance’, 2007.
\\Available: \href{www.cs.buap.mx/~dpinto/research/CICLing07_1/Pinto06c/node2.html}{\textcolor{blue}{\uline{www.cs.buap.mx/...}}} [Online]
\\(Accessed 27/11/2014)

\item Jean-Claude Latombe,
\\'Robot Motion Planning: Edition en anglais'. The Springer International Series in Engineering and Computer Science, Springer Science and Business Media, 1991 p.6, 22

\item D.V. Lu, D. Herschberger, W.D. Smart,
\\‘Layered Costmaps for Contest-Sensitive Navigation’, Washington University in St. Louis, Department of Computer Science and Engineering.
\\Available: \href{www.cse.wustl.edu/~dvl1/publications/LayeredCostmaps.pdf}{\textcolor{blue}{\uline{www.cse.wustl.edu...}}} [Online]
\\(Accessed 02/12/2014)

\item Zaman, S.; Slany, W.; Steinbauer, G.,
\\"ROS-based mapping, localization and autonomous navigation" Electronics, Communications and Photonics Conference (SIECPC), 2011 Saudi International , vol., no., pp.1,5, 24-26 April 2011 doi: 10.1109/SIECPC.2011.5876943. 
\\Available: \href{ieeexplore.ieee.org/xpls/icp.jsp?arnumber=5876943}{\textcolor{blue}{\uline{ieeexplore.ieee.org...}}} [Online]
\\(Accessed 02/12/2014)

\item ‘Pioneer P3-DX’,
\\Adept Mobile Robots,
\\Available: \href{mobilerobots.com/ResearchRobots/PioneerP3DX.aspx}{\textcolor{blue}{\uline{mobilerobots.com/...}}} [Online]
\\(Accessed 02/12/2014)

\item Scanning Range Finger (sokuiki sensor),
\\hokuyo-apt.jpt,
\\Available: \href{https://www.hokuyo-aut.jp/02sensor/07scanner/urg_04lx.html}{\textcolor{blue}{\uline{mhttps://www.hokuyo-aut.jp...}}} [Online]
\\(Accessed 02/12/2014)

\item M. Quigley, B. Gerkey, K. Conley, J. Faust, T. Foote, J. Leibs, E. Berger, R. Wheeler, A. Ng,
\\‘ROS: an open-source Robot Operating System’ Computer Science Department, University of Southern California. 
\\Available: \href{ai.stanford.edu/~ang/papers/icraoss09-ROS.pdf}{\textcolor{blue}{\uline{ai.stanford.edu.. .}}} [Online]
\\(Accessed 02/12/2014)

\item ‘What is ROS’,
\\ROS.org,
\\Available: \href{wiki.ros.org/ROS/Introduction}{\textcolor{blue}{\uline{wiki.ros.org/ROS/...}}} [Online]
\\(Accessed 02/12/2014)

\item ‘Navigation Package Summary’,
\\ROS.org,
\\Available: \href{wiki.ros.org/navigation}{\textcolor{blue}{\uline{wiki.ros.org/navigation}}} [Online]
\\(Accessed 02/12/2014)

\item Marder-Eppstein, E., Berger, E., Foote, T., Gerkey, B. and Konolige, K. (2010).
\\‘The Office Marathon: Robust navigation in an indoor office environment. 2010 IEEE International Conference on Robotics and Automation.’
\\Available: \href{wiki.ros.org/Papers/ICRA2010_Marder-Eppstein?action=AttachFile&do=view&target=icra2010_marder-eppstein.pdf}{\textcolor{blue}{\uline{wiki.ros.org/Papers...}}} [Online]
\\(Accessed 29/12/2014)

\item Bellotto, N. and Huosheng Hu, (2009).
\\‘Multisensor-Based Human Detection and Tracking for Mobile Service Robots’. IEEE Transactions on Systems, Man, and Cybernetics, Part B (Cybernetics), 39(1), pp.167-181. \\ Available: \href{webpages.lincoln.ac.uk/nbellotto/doc/Bellotto2009.pdf}{\textcolor{blue}{\uline{webpages.lincoln.ac.uk/...}}} [Online]
\\(Accessed 29/12/2014)

\item Beccera, M. (2012)
\\"Sistema De Seguimento de Personaspara un Robot Novil de Servicio". Universidad Nacional Autonoma De Mexico.
\\Available: \href{https://dl.dropboxusercontent.com/u/53733773/web/files/Becerra12_MEngThesis.pdf}{\textcolor{blue}{\uline{https://dl.dropboxuserco...}}} [Online]
\\(Accessed 29/12/2014)

\end{enumerate}
\end{document}